---
title: "Probability Theory"
---

# Assignment 1 

------------------------------------------------------------------------

> Given Probabilities -
 $P(S) = 0.3$, 
 $P(\overline{S}) = 0.7$, 
 $P(T/S) = 0.2$, 
 $P(\overline{T}/S) = 0.8$, 
 $P(T/\overline{S}) = 0.6$, 
 $P(\overline{T}/\overline{S}) = 0.4$



* $P(T\cap S) = P(S) * P(T/S)$

```{r}
P_T_and_S <- 0.3 * 0.2
P_T_and_S
```

* $P(T\cap \overline{S}) = P(\overline{S}) * P(T/\overline{S})$

```{r}
P_T_and_S_not <- 0.7 * 0.6
P_T_and_S_not
```

* $P(\overline{T}\cap S) = P(S) * P(\overline{T}/S)$

```{r}
P_not_T_and_S <- 0.3 * 0.8
P_not_T_and_S
```

* $P(\overline{T}\cap \overline{S}) = P(\overline{S}) * P(\overline{T}/\overline{S})$

```{r}
P_not_T_and_S_not <- 0.7 * 0.4
P_not_T_and_S_not
```

> Sum of all probabilities  

```{r}
sum <- P_T_and_S + P_T_and_S_not + P_not_T_and_S + P_not_T_and_S_not
sum
```

# Assignment 2

------------------------------------------------------------------------

* The percentage of customers using all three devices = 0.5%

* The percentage of customers using at least two devices 
  = 7.3 + 3.3 + 8.8 + 0.5 = 19.9% 

* The percentage of customers using only one device 
  = 42.3 + 27.8 + 10 = 80.1%

# Assignment 3

------------------------------------------------------------------------

> Given Probabilities - 
$P(B|A)=0.97$  
$P(B|\overline{A})=0.01$  
$P(A)=0.04$

By Bayesian Theorem,
$P(A|B) = \frac{P(A|B)*P(A)}{P(B)} = \frac{P(A|B)*P(A)}{P(B|A)*P(A)+P(B|\overline{A})*P(\overline{A})}$

> Probability that the product is not faulty

* $P(\overline{A}|B)$

```{r}
P_A_not_given_B = (0.01*0.96)/((0.01*0.96)+(0.97*0.04))
P_A_not_given_B_percentage = P_A_not_given_B * 100

paste("Probability that the product is not faulty -", P_A_not_given_B_percentage, "%")
```

> Probability that the product is faulty

* $P(A|B)$

```{r}
P_A_given_B = (0.97*0.04)/((0.01*0.96)+(0.97*0.04))
P_A_given_B_percentage = P_A_given_B * 100

paste("Probability that the product is faulty -", P_A_given_B_percentage, "%")
```

These results show that in case the alarm is triggered, there is a possibility of about `19.83%` that the product is flawless and a probability of `80.17%` that the product is faulty.
