---
title: "Randomized Controlled Trials"
---

------------------------------------------------------------------------

> Loading the data frame

```{r}
df  <- readRDS("Causal_Data_Science_Data/abtest_online.rds")
df
```

# Checking whether the covariates are balanced across the groups

```{r}
library(ggplot2)

compare_purchase_amount <- 
  ggplot(df, 
         aes(x = chatbot, 
             y = purchase_amount, 
             color = as.factor(chatbot))) +
  stat_summary(geom = "errorbar", 
               width = .5,
               fun.data = "mean_se", 
               fun.args = list(mult=1.96),
               show.legend = F) +
  labs(x = NULL, y = "purchase_amount", title = "Difference in purchase amount")
  compare_purchase_amount
```

::: callout-note
The two plots above show whether the different characteristics are balanced between the two groups.
:::

# Running a regression to find the effect of chatbot on sales.

```{r}
lm_sales_ate <- lm(purchase_amount ~ chatbot, data = df)
summary(lm_sales_ate)
```

::: callout-note
The coefficient of the chatbot is -7.0756, which means the presence of the chatbot has a negative influence on sales.
:::

# Finding subgroup-specific effects by including an interaction

```{r}
lm_cate4 <- lm(purchase_amount ~ chatbot + I(chatbot^2) * mobile_device + chatbot * previous_visit, data = df)
summary(lm_cate4)
```

::: callout-note
The above result gives the best R-squared value from the interaction I had.
:::

# Using the outcome variable purchase and runing a logistic regression.

```{r}
lm_model_binary <- glm(purchase ~ chatbot * mobile_device + chatbot * previous_visit, family = binomial(link = 'logit'), data = df)
summary(lm_model_binary)
```

::: callout-note
logistic regression is tailored for binary or categorical outcomes, and its interpretation revolves around odds ratios and probabilities.
:::