---
title: "Difference-in-Differences"
---

> Loading the data frame

```{r}
#| warning: false
library(dplyr)

df_hospdd  <- readRDS("Causal_Data_Science_Data/hospdd.rds")
df_hospdd
```

# Task - 1

------------------------------------------------------------------------

## Mean satisfaction for treated and control hospitals before and after the treatment

```{r}
# Step 1: Subset the data for treatment and control hospitals
treated_hospitals <- df_hospdd %>% filter(procedure == 1)
control_hospitals <- df_hospdd %>% filter(procedure == 0)

# Step 2: Compute mean satisfaction for treated hospitals before and after treatment
mean_satis_before_treated <- treated_hospitals %>%
  filter(month < 4) %>%
  pull(satis) %>%
  mean(na.rm = TRUE)
mean_satis_before_treated = 0

mean_satis_after_treated <- treated_hospitals %>%
  filter(month >= 4) %>%
  pull(satis) %>%
  mean(na.rm = TRUE)

# Step 3: Compute mean satisfaction for control hospitals before and after treatment
mean_satis_before_control <- control_hospitals %>%
  filter(month < 4) %>%
  pull(satis) %>%
  mean(na.rm = TRUE)

mean_satis_after_control <- control_hospitals %>%
  filter(month >= 4) %>%
  pull(satis) %>%
  mean(na.rm = TRUE)

# Step 4: Print the results
cat(
  "Mean Satisfaction -", "\n",
  "Before (Treated):", mean_satis_before_treated, "\n",
  "After (Treated):", mean_satis_after_treated, "\n",
  "Before (Control):", mean_satis_before_control, "\n",
  "After (Control):", mean_satis_after_control, "\n"
)
```

## DiD

```{r}
diff_before_treatment = mean_satis_before_treated - mean_satis_before_control
diff_after_treatment = mean_satis_after_treated - mean_satis_after_control

did_estimate <- diff_after_treatment - diff_before_treatment
did_estimate
```

# Task - 2

------------------------------------------------------------------------

## month + hospital

```{r}
model1<- lm(satis ~ month + hospital, data = df_hospdd)
model1
```

## as.factor(month) + as.factor(hospital)

```{r}
model2 <- lm(satis ~ as.factor(month) + as.factor(hospital), data = df_hospdd)
model2
```

> Difference:

* `month + hospital` treats them as continuous variables, while `as.factor(month) + as.factor(hospital)` treats them as categorical (factor) variables. The latter is more appropriate when dealing with factors like months and hospitals, where the order and magnitude might not have meaningful interpretations.

* For fixed effects representing categorical variables like months and hospitals, it is generally recommended to use `as.factor()` to ensure that the model considers them as discrete categories rather than continuous variables. This approach is more suitable for capturing the fixed effects accurately in the context of the analysis.